gtsummary

### 2020-12-18 rmarkdown-gtsummary.Rmd
updates

theme_gtsummary_compact()
set_gtsummary_theme(list(
  "as_gt-lst:addl_cmds" = list("cols_hide" = rlang::expr(gt::tab_options(table.font.names = "palatino")))
))
```

>>>>

# theme_gtsummary_compact()
# set_gtsummary_theme(list(
#   "as_gt-lst:addl_cmds" = list("cols_hide" = rlang::expr(gt::tab_options(table.font.names = "palatino")))
# ))

my_r_journal_theme <- theme_gtsummary_compact(set_theme = FALSE)
my_r_journal_theme$`as_gt-lst:addl_cmds` <-
  my_r_journal_theme$`as_gt-lst:addl_cmds` %>% 
  c(list("cols_hide" = rlang::expr(gt::tab_options(table.font.names = "palatino"))))

set_gtsummary_theme(my_r_journal_theme)
```
